Psychological Needs During Intergroup Contact: Three Experience Sampling Studies

### 2022-10-27 manuscript.tex
path figure added
re-render

% add packages
\usepackage[american]{babel}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{hyperref}
\usepackage[style=apa, sortcites=true, sorting=nyt, backend=biber, natbib=true, uniquename=false, uniquelist=false, useprefix=true]{biblatex}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{setspace,caption}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{soul}
\usepackage{xcolor}
\usepackage{fourier}
\usepackage{stackengine}
\usepackage{scalerel}
\usepackage{fontawesome5}
\usepackage[normalem]{ulem}
% \usepackage{longtable}
\usepackage{amsmath}
\usepackage{ntheorem}
\usepackage{afterpage}
\usepackage{float}
\usepackage{array}
\usepackage{censor}
\usepackage{pdflscape}
\usepackage{lscape}
\usepackage{pdfpages}
\usepackage{enumitem}
\usepackage{caption}
\usepackage{adjustbox}
\usepackage{makecell}
\usepackage{tabu}

@@

% Figures
\begin{figure}
  \caption{Contact Hypothesis}
  \label{fig:ContactHypothesis}
  \centering\includegraphics[width=\textwidth]{Figures/forestParametricREMLGeneralLmer.png}
  %\begin{subfigure}{\textwidth}
  %  \caption{}
  %  \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricGeneralLm.png}
  %\end{subfigure}
  %\begin{subfigure}{\textwidth}
  %  \caption{}
  %  \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricFEGeneralLmer.png}
  %\end{subfigure}
  \caption*{Note: \\
  Summary of mixed models results of the contemporaneous contact effects.\\
  General: Random effects meta analytic results are presented for completeness.}
\end{figure}

>>>>

% add packages
\usepackage[american]{babel}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{hyperref}
\usepackage[style=apa, sortcites=true, sorting=nyt, backend=biber, natbib=true, uniquename=false, uniquelist=false, useprefix=true]{biblatex}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{setspace,caption}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{soul}
\usepackage{xcolor}
\usepackage{fourier}
\usepackage{stackengine}
\usepackage{scalerel}
\usepackage{fontawesome5}
\usepackage[normalem]{ulem}
% \usepackage{longtable}
\usepackage{amsmath}
\usepackage{ntheorem}
\usepackage{afterpage}
\usepackage{float}
\usepackage{array}
\usepackage{censor}
\usepackage{pdflscape}
\usepackage{lscape}
\usepackage{pdfpages}
\usepackage{enumitem}
\usepackage{caption}
\usepackage{adjustbox}
\usepackage{makecell}
\usepackage{tabu}
% Path Diagrams
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.17}
\tikzset{mynode/.style={draw,text width=1in,align=center} }
\usetikzlibrary{positioning}

@@

% Figures
\begin{figure}
  \caption{Path Diagrams Situational Needs Model across Studies}
  \label{fig:MainPaths}
  \begin{center}
    \input{PathModels.tex}
  \end{center}
  \caption*{Note: \\
  (A) Study 1; (B) Study 2; (C) Study 3.\\
  General: Path coefficients are standardized regression coefficients. Statistical significance markers are based on the unstandardized regression results (as presented in Table \ref{tab:intergroupNeedsTblLong}).\\
  **** p < .0001, *** p < .001, ** p < .01, * p < .05}
\end{figure}

\begin{figure}
  \caption{Contact Hypothesis}
  \label{fig:ContactHypothesis}
  \centering\includegraphics[width=\textwidth]{Figures/forestParametricREMLGeneralLmer.png}
  %\begin{subfigure}{\textwidth}
  %  \caption{}
  %  \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricGeneralLm.png}
  %\end{subfigure}
  %\begin{subfigure}{\textwidth}
  %  \caption{}
  %  \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricFEGeneralLmer.png}
  %\end{subfigure}
  \caption*{Note: \\
  Summary of mixed models results of the contemporaneous contact effects.\\
  General: Random effects meta analytic results are presented for completeness.}
\end{figure}
